The Negative Effect of Traffic Noise on House Prices: A Landscape Hedonic Analysis

### 2013-09-30 reports/Draft.Rnw

In this paper, we seek to contribute to the noise hedonic literature by examining the relationship between single family home prices from 2005 to 2010 and variation in road traffic noise exposure in the St.\ Paul, Minnesota urban area. Our work makes multiple contributions to the field. First, we utilize new estimates of traffic noise that have never before been used in the hedonic literature. The noise propagation model estimates traffic noise levels at a high spatial resolution (10m x 10m) while also incorporating the effects of nearby buildings and landcover.

>>>>

In this paper, we contribute to the noise hedonic literature by examining the relationship between single family home prices from 2005 to 2010 and variation in road traffic noise exposure in the St.\ Paul, Minnesota urban area across 44 different cities. First, we utilize new estimates of traffic noise that have never before been used in the hedonic literature. The noise propagation model estimates traffic noise levels at a high spatial resolution (10m x 10m) while also incorporating the effects of nearby buildings and landcover.
